---
title: "new_all"
output: html_document
date: "2024-01-02"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Packages
```{r}
library(ggplot2)
library(dplyr) 
library(ggpubr)
library(showtext)
library(tidyr)
library(vegan)
library(glmmTMB)
library(Hmisc)
library(emmeans)
library(DHARMa)
library(lme4)
library(ggsignif)
library(ggpattern)
```
Monitoring data
```{r}
survey <- read.csv2("new_raw_data.csv",header=TRUE,sep=";",dec=".")
survey$transect_id<-as.character(survey$transect_id)
survey <- survey %>%
  mutate(date = as.Date(date,format="%d.%m.%Y"))
survey$method <-factor(survey$method,levels=c("cam","walk1","walk2"))
```

Nb of observations of each methods
```{r}
group_by(survey,method)%>%
  summarise(count = sum(!is.na(species)))
```


Total nb of species detected by each method
```{r}
print(survey_summary<-survey%>%
  group_by(method)%>%
     summarise(n_unique = n_distinct(species, na.rm = TRUE)))
```
Spp detected by cameras but not transect sampling
```{r}
exclusive_cam <- survey %>%
  filter(method == "cam") %>%
  pull(species)
exclusive_walk1 <- survey %>%
  filter(method == "walk1") %>%
  pull(species)
exclusive_walk2 <- survey %>%
  filter(method == "walk2") %>%
  pull(species)
print(setdiff(exclusive_cam, exclusive_walk1))
print(setdiff(exclusive_cam, exclusive_walk2))
```
Expected spp that were not detected
```{r}
exclusive_exp <- expected_sp %>%
  pull(species)
print(setdiff(exclusive_exp, exclusive_cam))
print(setdiff(exclusive_exp, exclusive_walk1))
print(setdiff(exclusive_exp, exclusive_walk2))
```
Nb of species detected by each method
```{r}
#Nb of observed spp detected per method
ratio<-survey %>%
   filter(!is.na(species)) %>%
  filter(method %in% c("cam", "walk2")) %>%
 group_by(method) %>%
summarise(n_species = n_distinct(species))

#Making the graph
custom_labels <- c("Camera Trapping", "Transect Sampling")

print(ggplot(ratio, aes(x = method, y = n_species, fill=method)) +
        ylim(0,40)+
  geom_bar(stat = "identity",width=0.5) +
   theme_classic()+
    scale_x_discrete(labels = custom_labels)+
  scale_fill_manual(values = c("cam"="black","walk2"="red"))+
   theme(axis.title.x = element_blank(),axis.title.y = element_text(size = 30), axis.text.x = element_text(color = "black"),axis.text.y = element_text(color = "black"),text=element_text(size=30, family="serif"))+
  ylab("No. of Species")+
  guides(fill=FALSE))
ggsave("n_sp.png",height=8,width = 16)
```

Top 3 spp. most often detected, according to each method
```{r}
print(survey%>%
  filter(method == "cam") %>%
  count(species) %>%
  top_n(3, wt = n))

print(survey%>%
  filter(!is.na(species),method == "walk1") %>%
  count(species) %>%
  top_n(3, wt = n))

print(survey%>%
  filter(!is.na(method),method == "walk2") %>%
  count(species) %>%
  top_n(3, wt = n))
```
Species accumulation curves
```{r}
#Loading community data (i.e. data with nb of detection per transect walk)
com_walk1 <- read.csv2("community_data_walk1.csv")
com_walk1 <- replace(com_walk1, is.na(com_walk1), 0)

com_walk2 <- read.csv2("community_data_walk2.csv")
com_walk2 <- replace(com_walk2, is.na(com_walk2), 0)

#For camera trapping: creating the community dataset with species as columns and nb of occurrences as values, and counting the nb of occurrence of each species
cam_count<-survey%>%
  filter(method=="cam")%>%
  group_by(date,species)%>%
  summarise(count = n())%>%
  pivot_wider(names_from=species,values_from=count,values_fill=0)
cam_count<-subset(cam_count,select=-1)

#Adding the missing expected species with 0 as values
expected_sp <- read.csv2("expected_species.csv")
expected_sp$count <- 0
com_exp <- expected_sp%>%
  subset(select=-c(1,3))%>%
  pivot_wider(names_from=species,values_from=count)
merged_cam <- full_join(cam_count, com_exp) %>%
  replace(is.na(.), 0)
merged_cam <- merged_cam[-nrow(merged_cam),]

#Richness obtained by each method
richnesswalk1<-specaccum(com_walk1)
richnesswalk2<-specaccum(com_walk2)
richnesscam<-specaccum(merged_cam)


png(filename="SAC.png",width=950, height=750)
par(family = "serif", cex=2)
plot(richnesswalk1,xlab = "No. of Sampling Units", ylab = "No. of Species",bty="l",ylim = c(0,23),lwd=3)
#lines(richnesswalk2,lty=3,lwd=5)
#lines(richnesscam,lty=5,lwd=5)
lines(richnesswalk2,lwd=2,col="red",lty=2)
lines(richnesscam,lwd=2,col="black")
lines(richnesswalk1,lwd=2,col="red")
legend("bottomright",box.lwd = 0,bty = "n", bg = "transparent",legend = c("Camera Trapping", "Transect Sampling (1 Obs.)", "Transect Sampling (2 Obs.)"),col=c("black","red","red"), lwd = 2,lty=c(1,1,2))
dev.off()
```
Costs
```{r}
cost_data <- read.csv2("new_data_cost.csv")
cost_data$cost_chf <- as.numeric(cost_data$cost_chf)
cost_data$cost_zar <- as.numeric(cost_data$cost_zar)
```
Proportion of money spent on XYZ
```{r}
cam_costzar<-cost_data%>%
  filter(method=="cam")%>%
select(type, cost_zar)%>%
  mutate(proportion =round(cost_zar/sum(cost_zar) * 100,2))

walk1_costzar<-cost_data%>%
  filter(method=="walk1")%>%
  select(type, cost_zar)%>%
  mutate(proportion =round(cost_zar/sum(cost_zar) * 100,2))

walk2_costzar<-cost_data%>%
  filter(method=="walk2")%>%
  select(type, cost_zar)%>%
  mutate(proportion =round(cost_zar/sum(cost_zar) * 100,2))
```

Nb of days sampled by both methods
```{r}
survey_days_walk <- 38
survey_days_cam <- 62
sum_expenses <- cost_data%>%
  group_by(method)%>%
  summarise(total_zar=sum(cost_zar),total_chf=sum(cost_chf))
```
Estimated cost/day IN CHF for 1 survey of 60 days
```{r}
x_1 <- seq(1, 60, length.out = 60) #nb of survey days

equipment_cost_cam <- cost_data$cost_chf[cost_data$type=="equipment"& cost_data$method == "cam"]
prep_cost_cam <- cost_data$cost_chf[cost_data$type=="preparation"& cost_data$method == "cam"]
data_cost_cam <- cost_data$cost_chf[cost_data$type=="data_analysis"&cost_data$method == "cam"]
maintenance_cam <- 29.49595512 #cost of maintenance (fieldwork, car usage), which will be pro rated depending on nb of survey days 
field_cost_cam <- cost_data$cost_chf[cost_data$type=="fieldwork"&cost_data$method == "cam"]-maintenance_cam #price of fieldwork - maintenance (since it will be pro-rated)

  
y_cam <- (equipment_cost_cam + prep_cost_cam+(maintenance_cam/ survey_days_cam)*x_1+(data_cost_cam/ survey_days_cam)*x_1+ field_cost_cam)/x_1 #price per survey day (y) depending on nb of days (x), with equipment, prep and fieldwork (except for maintenance) costs as fixed costs for CT and maintenance as "pro rata" costs

equipment_cost_walk <- cost_data$cost_chf[cost_data$type=="equipment"& cost_data$method == "walk"]
prep_cost_walk <- cost_data$cost_chf[cost_data$type=="preparation"& cost_data$method == "walk"]
data_cost_walk <- cost_data$cost_chf[cost_data$type=="data_analysis"&cost_data$method == "walk"]
field_cost_walk <- cost_data$cost_chf[cost_data$type=="fieldwork"&cost_data$method == "walk"]

y_walk <- (equipment_cost_walk + prep_cost_walk+(data_cost_walk/ survey_days_walk) * x_1 + (field_cost_walk / survey_days_walk)*x_1) / x_1

# Combine the data into a single data frame
data_combined1 <- data.frame(
  x = x_1,
  y = c(y_cam, y_walk),
  method = rep(c("cam", "walk"), each = 60))

#Create the function plot
print(ggplot(data_combined1, aes(x = x, y = y,color=method)) +
  geom_line(size=1.2)+
    theme_classic()+
    scale_color_manual(values = c("cam" = "black", "walk" = "red"),labels=c("Camera Trapping","Transect Sampling"))+
  labs(x = "No. of Survey Days",
       y = "Cost per Survey Day (CHF)")+
     theme(axis.title.x = element_text(size = 30),axis.title.y = element_text(size = 30), axis.text.y = element_text(color = "black"),axis.text.x = element_text(color = "black"),text=element_text(size=30, family="serif"),legend.title=element_blank(),legend.text=element_text(color="black",size=30,family="serif"))+
  scale_x_continuous(breaks = seq(0, max(data_combined1$x), by = 5)) +
  scale_y_continuous(breaks = seq(0, max(data_combined1$y), by = 500)))
ggsave("f_costs.png",height=8,width = 16)

```
Zooming in
```{r}
print(ggplot(data_combined1, aes(x = x, y = y,color=method)) +
        coord_cartesian(ylim=c(1,600))+
  geom_line(size=1.2)+
    theme_classic()+
    scale_color_manual(values = c("cam" = "black", "walk" = "red"),labels=c("Camera Trapping","Transect Sampling"))+
  labs(x = "No. of Survey Days",
       y = "Cost per Survey Day (CHF)")+
     theme(axis.title.x = element_text(size = 30),axis.title.y = element_text(size = 30), axis.text.y = element_text(color = "black"),axis.text.x = element_text(color = "black"),text=element_text(size=30, family="serif"),legend.title=element_blank(),legend.text=element_text(color="black",size=30,family="serif"))+
  scale_x_continuous(breaks = seq(0, max(data_combined1$x), by = 5)) +
  scale_y_continuous(breaks = seq(0, max(data_combined1$y), by = 100)))
ggsave("f_costs_zoom.png",height=8,width = 16)
```


Data for models
```{r}
xdata <- read.csv2("data_cam_transect_diurnal.csv",header=TRUE,sep=";",dec=".")
xdata$transect_id<-as.character(xdata$transect_id)
xdata$habitat_type<-as.character(xdata$habitat_type)
xdata$length_m<-as.numeric(xdata$length_m)
```
Putting all character predictors as factors 
```{r}
xdata$method <- as.factor(xdata$method)
xdata$habitat_type <- as.factor(xdata$habitat_type)
xdata$transect_id <- as.factor(xdata$transect_id)
```

Model 1: nb of independent sightings
Count data (i.e. integers and 0-bounded) so we will first fit a model with Poisson distribution
Has to be a GLMM because spatial correlation+unbalanced design (i.e. not same sample sizes between treatments)+ random effect (transect ID). We will do a GLMM with an offest due to uneven sampling effort.
First, checking the model's assumption for absence of multicollinearity, so checking the correlation of environmental predictors
```{r}
num_predictors = c("precip","tempmax","cloudcover")
df <- xdata%>%
  select(all_of(num_predictors))
print(df.cor <- rcorr(as.matrix(df)))
```
Environmental explanatory variables are highly correlated, so we will need to select which one makes sense to keep because they cannot be used together.
```{r}
m_sight<-glmer(n_sightings~method+habitat_type+ offset(log(eff_time_h))+(1|transect_id),family="poisson",data=xdata )
summary(m_sight)

m_sight1<-glmer(n_sightings~method+habitat_type+tempmax+ offset(log(eff_time_h))+(1|transect_id),family="poisson",data=xdata )
summary(m_sight1)

m_sight2<-glmer(n_sightings~method+habitat_type+precip+ offset(log(eff_time_h))+(1|transect_id),family="poisson",data=xdata )
summary(m_sight2)

m_sight3<-glmer(n_sightings~method+habitat_type+cloudcover+ offset(log(eff_time_h))+(1|transect_id),family="poisson",data=xdata )
summary(m_sight3)
```
Precipitation model produces the best estimate (almost equivalent to model wihtout any meteorological variable) so we will keep this variable

Now we need to check if the data is zero inflated
```{r}
colSums(xdata==0)#checking the nb of 0s in our variable
nrow(xdata)
```

```{r}
run_function <- function(){
  poispois<- rpois(n=length(residuals(m_sight2)), lambda=fitted(m_sight2))
  value <- sum(poispois==0)
}

x <- replicate(1000, run_function())
head(x)

hist(x, breaks = 50, main="Number of 0s in the reponse given the poisson model")
abline(v=37, col="red")#adding a line corresponding to our amount of 0s
```
Not zero-inflated
```{r}
png(file="dispersion1_m_sightings.png",width=800, height=350)
plot(simulateResiduals(m_sight2))
dev.off()
```
Overdispersion issue so we need to account for that by computing a quasi-poisson model 
```{r}
quasi<-glmmTMB(n_sightings~method+habitat_type+precip+ offset(log(eff_time_h))+(1|transect_id),family=nbinom1,data=xdata )
plot(simulateResiduals(quasi))
```
Issue is still not resolved so giving an observation-level random effect 
```{r}
m_test<-glmer(n_sightings~method+habitat_type+precip+ offset(log(eff_time_h))+(1|transect_id)+(1|walk_number),family=poisson,data=xdata )
summary(m_test)

png(file="dispersion3_m_sightings.png",width=800, height=350)
plot(simulateResiduals(m_test))
dev.off()
```
Resolved the issue
Comparing our model to a null model
```{r}
null <-glmer(n_sightings~1+ offset(log(eff_time_h))+(1|transect_id)+(1|walk_number),family="poisson",data=xdata )
summary(null)
anova(m_test,null,test="Chisq")
```
Chi-square strongly significant so we can keep this model and interpret it
```{r}
drop1(m_test,test="Chisq")
```
The method and habitat type strongly and significantly influences the nb of sightings per camera station or transect walked. Now we do a post-hoc test (Estimated marginal means/EMMs) to investigate within group differences
```{r}
emmeans(m_test,specs=pairwise~method,type="response")
emmeans(m_test,specs=pairwise~habitat_type,type="response")
```
Method cam and both types of walks significantly differ. The difference is more important between cam and walk2 than cam and walk1 (z.ratio). The difference between walk1 and walk2 is not statistically significant.
There is a significant difference between the nb of species sighted in habitat 3 compared to all other habitats, of approximately the same magnitude.

Graphs
```{r}
graphdata <- read.csv2("graph_data_cam_transect_diurnal.csv") #same dataset but with walk 1 and 2 merged for the graph
graphdata$transect_id<-as.character(graphdata$transect_id)
graphdata$habitat_type<-as.character(graphdata$habitat_type)
graphdata$length_m<-as.numeric(graphdata$length_m)
graphdata$method <- as.factor(graphdata$method)
graphdata$habitat_type <- as.factor(graphdata$habitat_type)
graphdata$transect_id <- as.factor(graphdata$transect_id)

custom_labels <- c("Camera Trapping", "Transect Sampling")

print(ggplot(data=graphdata, aes(x=method, y=n_sightings,fill=method,pattern=method)) +
  geom_boxplot(outlier.size = 2.3)+
    ylab("No. of Independent Observations")+
  ylim(0,230)+
           geom_jitter(color="black", size=1, alpha=0.9) +
    scale_x_discrete(labels = c("cam" = "Camera Trapping", "walk" = "Transect Sampling"))+
       theme_classic()+
    theme(axis.title.x = element_blank(),axis.title.y = element_text(size = 30),axis.text.y = element_text(color = "black"),axis.text.x = element_blank(),text=element_text(size=30,color="black", family="serif"))+
  guides(fill = guide_legend(title = NULL))+
    geom_signif(stat="signif",position="identity",comparisons = list(c("cam", "walk")),map_signif_level=TRUE,color = "black",annotations="***",y_position=205,textsize=8.5)+  scale_fill_manual(labels = custom_labels, values = c("cam"="gray28","walk"="red"))+
  guides(fill = guide_legend(title = NULL))+theme(legend.position = "none"))

ggsave("m_sightings.png",height=8,width = 16)

print(ggplot(data=xdata, aes(x=habitat_type, y=n_sightings,fill=habitat_type)) +
  geom_boxplot(outlier.size = 2.5)+
    ylab("No. of Independent Observations")+
  theme_classic()+
    ylim(0,230)+
    scale_x_discrete(labels = c("1"="Woodland","2"="Thicket","3"="Closed Thicket","4"="Road"))+
            geom_jitter(color="black", size=1.2, alpha=0.7)+
    geom_signif(stat="signif",position="identity",comparisons = list(c("3", "1")),map_signif_level=TRUE,color = "black",annotations="***",y_position=210,textsize = 11)+
    geom_signif(stat="signif",position="identity",comparisons = list(c("3", "2")),map_signif_level=TRUE,color = "black",annotations="***",y_position=195,textsize = 11)+
    geom_signif(stat="signif",position="identity",comparisons = list(c("3", "4")),map_signif_level=TRUE,color = "black",annotations="***",y_position=185,textsize = 11)+
  theme(axis.title.y = element_text(size = 37),axis.title.x = element_blank(), axis.text.y = element_text(color = "black"),axis.text.x = element_blank(),text=element_text(size=37, family="serif"))+
  scale_fill_manual(values = c("1"="sienna","2"="olivedrab3","3"="darkgreen","4"="grey"))+theme(legend.position = "none")+
  guides(fill = guide_legend(title = NULL)))
ggsave("m_sight_hab.png",height=10,width = 20)

```

Summary table of the model
```{r}
sjPlot::tab_model(m_test,file = "m_sight_table.doc")
```


Model 2: nb of species detected
```{r}
m_n_sp <- glmer(n_species_detected~method+habitat_type+ offset(log(eff_time_h))+(1|transect_id),family=poisson,data=xdata )
summary(m_n_sp)

m_n_sp1<-glmer(n_species_detected~method+habitat_type+tempmax+ offset(log(eff_time_h))+(1|transect_id),family=poisson,data=xdata )
summary(m_n_sp1)

m_n_sp2<-glmer(n_species_detected~method+habitat_type+precip+ offset(log(eff_time_h))+(1|transect_id),family=poisson,data=xdata )
summary(m_n_sp2)

m_n_sp3<-glmer(n_species_detected~method+habitat_type+cloudcover+ offset(log(eff_time_h))+(1|transect_id),family=poisson,data=xdata )
summary(m_n_sp3)
```
Precipitation model produces the best estimate so we will keep it (almost equivalent without any meteorological predictor)

Now we need to check if the data is zero inflated
```{r}
colSums(xdata==0)#checking the nb of 0s in our variable
nrow(xdata)

run_function <- function(){
  poispois<- rpois(n=length(residuals(m_n_sp2)), lambda=fitted(m_n_sp2))
  value <- sum(poispois==0)
}

x <- replicate(1000, run_function())
head(x)

hist(x, breaks = 50, main="Number of 0s in the reponse given the poisson model")
abline(v=37, col="red")#adding a line corresponding to our amount of 0s
```
The nb of 0s of our data falls within the expected nb of zeroes for Poisson distributed data, so our data is not zero-inflated.
Plotting the fitted residuals to see if our model is good
```{r}
plot(simulateResiduals(m_n_sp2))
```
No over dispersion but residuals not fitting very well, but not worrisome because we have good estimates with small SE values

Comparing our model to a null model
```{r}
nullpoiss <-glmer(n_species_detected~1+ offset(log(eff_time_h))+(1|transect_id),family=poisson,data=xdata )
anova(m_n_sp2,nullpoiss,test="Chisq")
```
ANOVA strongly significant so we can keep this model and interpret it
```{r}
drop1(m_n_sp2,test="Chisq")
```
The method strongly and significantly influences the nb of species detected per hour invested into the survey; the habitat also significantly influences the nb of species detected per hour invested into the survey, but less. Now we do a post-hoc test (Estimated marginal means/EMMs) to check group differences
```{r}
emmeans(m_n_sp2,specs=pairwise~method,type="response")
emmeans(m_n_sp2,specs=pairwise~habitat_type,type="response")
```
Method cam and both types of method walk significantly differ. The difference is more important between cam and walk2 than cam and walk1 (z.ratio). The difference between walk1 and walk2 is not statistically significant.
There is a significant difference between the nb of species sighted in habitat 3 compared to habitat 2 and 4, of approximately the same magnitude.

Graphs:
```{r}
print(ggplot(data=graphdata, aes(x=method, y=n_species_detected,fill=method)) +
  geom_boxplot(outlier.size = 2.3)+
    ylab("No. of Species")+
    theme_classic()+
    geom_jitter(color="black", size=1, alpha=0.9) +
    scale_x_discrete(labels = c("cam" = "Camera Trapping", "walk" = "Transect Sampling"))+
    theme(axis.title.x = element_blank(),axis.text.x = element_blank(),axis.title.y = element_text(size = 30), axis.text.y = element_text(color = "black"),text=element_text(size=30, family="serif"))+
  guides(fill = guide_legend(title = NULL))+
    ylim(0,15)+
    geom_signif(stat="signif",position="identity",comparisons = list(c("cam", "walk")),map_signif_level=TRUE,color = "black",annotations="***",textsize=8.5)+
  scale_fill_manual(labels = custom_labels, values = c("cam"="gray28","walk"="red"))+theme(legend.position = "none"))

ggsave("m_n_sp.png",height=8,width = 16)

   
print(ggplot(data=xdata, aes(x=habitat_type, y=n_species_detected,fill=habitat_type)) +
  geom_boxplot(outlier.size = 2.5)+
    xlab("Habitat")+
    ylab("No. of Species")+
    theme_classic()+
    ylim(0,15)+
    scale_x_discrete(labels = c("1"="Woodland","2"="Thicket","3"="Closed Thicket","4"="Road"))+
        geom_jitter(color="black", size=1.2, alpha=0.9) +
    geom_signif(stat="signif",position="identity",comparisons = list(c("2", "3")),map_signif_level=TRUE,annotations="**",textsize=11)+
    geom_signif(stat="signif",position="identity",comparisons = list(c("3", "4")),map_signif_level=TRUE,annotations="**",y_position = 13.5,textsize=11)+
   theme(axis.title.y = element_text(size = 37),axis.title.x = element_blank(), axis.text.y = element_text(color = "black"),axis.text.x = element_text(color = "black"),text=element_text(size=37, family="serif"))+
  scale_fill_manual(values = c("1"="sienna","2"="olivedrab3","3"="darkgreen","4"="grey"))+theme(legend.position = "none")+
  guides(fill = guide_legend(title = NULL)))

ggsave("m_n_sp_hab.png",height=10,width = 20)
```

Summary table of the model
```{r}
sjPlot::tab_model(m_n_sp2,file = "m_sp_table.doc")
```


Model 3: average body mass of spp detected
First we need to remove NAs because body mass cannot be 0
```{r}
xdata_naomit <- xdata[complete.cases(xdata$mean_weight_animal_detected), ]
```
Checking the data distribution
```{r}
hist(xdata_naomit$mean_weight_animal_detected)
```
Spatial correlation+unbalanced design+random effect= GLMM without zero-inflation (bc no 0s). We will try a gamma model because response variable seems to have a chi-squared distribution. We add the sampling effort as a weight
```{r}
m_weight <-glmer(mean_weight_animal_detected~method+habitat_type+ (1|transect_id),family=Gamma(link="log"),weights = eff_time_h,data=xdata_naomit)
summary(m_weight)

m_weight1 <-glmer(mean_weight_animal_detected~method+habitat_type+tempmax+ (1|transect_id),family=Gamma(link="log"),weights = eff_time_h,data=xdata_naomit)
summary(m_weight1)

m_weight2 <-glmer(mean_weight_animal_detected~method+habitat_type+precip+ (1|transect_id),family=Gamma(link="log"),weights = eff_time_h,data=xdata_naomit)
summary(m_weight2)

m_weight3 <-glmer(mean_weight_animal_detected~method+habitat_type+cloudcover+ (1|transect_id),weights = eff_time_h,family=Gamma(link="log"),data=xdata_naomit)
summary(m_weight3)
```
Precipitation has the strongest explanatory power. We will now compare the fit of this model's residuals compared to a Gaussian GLMM to see if gamma is actually suitable
```{r}
m_weight_normal <-glmmTMB(mean_weight_animal_detected~method+habitat_type+tempmax+ (1|transect_id),weights = eff_time_h,data=xdata_naomit)
plot(simulateResiduals(m_weight_normal))

plot(simulateResiduals(m_weight2))
```
Plotting the scaled residuals showed no issue with the model. Now we need to compare the model to a null model to see if it is actually good
```{r}
null_weight <-glmer(mean_weight_animal_detected ~ 1 +(1 | transect_id),weights = eff_time_h,data = xdata_naomit, family=Gamma(link = "log"))

anova(m_weight2, null_weight, test="Chisq")
```

ANOVA strongly significant so we can keep this model and interpret it
```{r}
drop1(m_weight2,test="Chisq")
```
The method strongly and significantly influences the nb of species detected per hour invested into the survey; the habitat also significantly influences the nb of species detected per hour invested into the survey, but less. Now we do a post-hoc test (Estimated marginal means/EMMs) to check group differences

```{r}
emmeans(m_weight2,specs=pairwise~method,type="response")
emmeans(m_weight2,specs=pairwise~precip,type="response")

```
Significant difference between walk1 and walk2. Precipitation has a significant impact, in that the more precipitation was recorded the larger the species detected.

Graphs
```{r}
graph_naomit <- graphdata[complete.cases(graphdata$mean_weight_animal_detected), ]
graph_naomit$mean_weight_animal_detected <- as.numeric(graph_naomit$mean_weight_animal_detected)

print(ggplot(data=graph_naomit, aes(x=method, y=mean_weight_animal_detected,fill=method)) +
  geom_boxplot(outlier.size = 2.3)+
    ylab("Body Mass of Animals Detected (kg)")+
  theme_classic()+
    ylim(0,1300)+
    theme(axis.title.x = element_blank(),axis.title.y = element_text(size = 30), axis.text.y = element_text(color = "black"),axis.text.x = element_text(color = "black"),text=element_text(size=30, family="serif"))+
     scale_x_discrete(labels = c("cam" = "Camera Trapping", "walk" = "Transect Sampling"))+
         geom_jitter(color="black", size=1, alpha=0.9) +
  scale_pattern_manual(values=c("none","none"))+
  scale_fill_manual(values = c("cam"="gray28","walk"="red"))+
    theme(legend.position = "none"))
ggsave("m_weight.png",height=8,width = 16)

```

Summary table of the model
```{r}
sjPlot::tab_model(m_weight2,file = "m_weight_table.doc")
```
